---
title: "linear regression"
author: "qingqi he"
date: "4/18/2022"
output: html_document
---

```{r, message=FALSE, warning=FALSE, include=FALSE}
require(MASS)
require(glmnet)
library(kableExtra)
library(stargazer)
library(flextable)
library(dplyr)
library(leaps)
library(caret)
library(ggplot2)
library(ggExtra)
library(tidyr)
library(ISLR2)
library(ISLR)
library(readr)
library(reticulate)
library(sjPlot)
if (!require("pacman")) install.packages("pacman")
pacman::p_load("weights", "interactions", "cjoint", "plm", "interactions", "jtools", "stats", "miceadds", "broom", "RColorBrewer", "ggstatsplot", "ggpubr", "stargazer", "sandwich", "hrbrthemes", "rms", "interplot", "coefplot", "gmodels", "car", "lattice","foreign", "ggplot2", "MASS", "Hmisc", "reshape2", "oddsratio", "tidyr", "psych", "dplyr", "tidyverse", "cjoint")

knitr::opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE,echo = TRUE)

def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```


# Clara's data
```{r}
setwd("/Users/qingqihe/georgetown/512")
data <- read_csv("ANLY-512/More_Variables_Cleaned.csv")
data2 <- read_csv("ANLY-512/data_from_worldbank.csv")
data2 <- data2[,c(1,2,3,4)]

kable(head(data)) %>% kable_styling(bootstrap_options = "striped", full_width = F, position = "center")
```




```{r}
# Change the variable type
data$Country <- as.factor(data$Country)
data$Same_sex_marriage <- as.factor(data$Same_sex_marriage)
data$Year <- as.factor(data$Year)
```

## split the dataset and exclude country and year
```{r}
set.seed(24516)
data_exCY <- data[,-c(1,2)]
train_sample <-createDataPartition(data_exCY$Marriage_rate,p = 0.8, list = F)
train_data <- data_exCY[train_sample,]
test_data <- data_exCY[-train_sample,]

```



# Model 1 (exclude the country and year)
```{r}
fit1 <- lm(Marriage_rate~., data = train_data)
summary(fit1)
```


# Exclude the not significant variable
```{r}

fit2 <- lm(Marriage_rate ~.-Same_sex_marriage-average_years_of_schooling_of_women_in_reproductive_age , data = train_data)
summary(fit2)

```


# Check the multicollinearity
```{r}
VIF_art <- data.frame(car::vif(fit2))
VIF_art %>% kbl() %>% kable_styling(bootstrap_options = "striped", 
                                          full_width = F, position = "center")
```


```{r}
fit3 <- lm(Marriage_rate~(Male_Life_Expectancy + female_Life_Expectancy+ GDP + Births_outside_marriage + Divorce_rate + Estimated_average_age_at_marriage_women + births_per_woman + Population_est)^2 , data = train_data)
summary(fit3)
```

## Since vif tell us that life expentency have high multicollinearity ,remove man expentency variable first
```{r}
fit4 <- lm(Marriage_rate~female_Life_Expectancy + GDP + Births_outside_marriage + Divorce_rate + Estimated_average_age_at_marriage_women + births_per_woman + Population_est, data = train_data)

summary(fit4)

```

# Check the multicollinearity again
```{r}
VIF_art2 <- data.frame(car::vif(fit4))
VIF_art2 %>% kbl() %>% kable_styling(bootstrap_options = "striped", 
                                          full_width = F, position = "center")

```

# Now let's see which model the better
```{r}
pre1 <- fit1 %>% predict(test_data)
p1 = data.frame(RMSE = RMSE(pre1, test_data$Marriage_rate),R2 = R2(pre1,test_data$Marriage_rate))

pre2 <- fit2 %>% predict(test_data)
p2 = data.frame(RMSE = RMSE(pre2, test_data$Marriage_rate),R2 = R2(pre2,test_data$Marriage_rate))

pre3 <- fit3 %>% predict(test_data)
p3 = data.frame(RMSE = RMSE(pre3, test_data$Marriage_rate),R2 = R2(pre3,test_data$Marriage_rate))

pre4 <- fit4 %>% predict(test_data)
p4 = data.frame(RMSE = RMSE(pre4, test_data$Marriage_rate),R2 = R2(pre4,test_data$Marriage_rate))
```

```{r}
all = rbind(p1,p2,p3,p4)
# add F-statistic
all = cbind(all, c(summary(fit1)$fstatistic[1],summary(fit2)$fstatistic[1],summary(fit3)$fstatistic[1],summary(fit4)$fstatistic[1]))
# add adj r squared
all = cbind(all, c(summary(fit1)$adj.r.squared,summary(fit2)$adj.r.squared,summary(fit3)$adj.r.squared,summary(fit4)$adj.r.squared))
#add RSE
all = cbind(all, c(summary(fit1)$sigma,summary(fit2)$sigma,summary(fit3)$sigma,summary(fit4)$sigma))

all = cbind(c('fit1','fit2','fit3','fit4'),all)
colnames(all)[c(1,4,5,6)] <- c('models','F stat', 'adj.r2','RSE')

all
```









# Now test my merge dataset

```{r}
# merge the data
newdata <- merge(data,data2, all.x = TRUE)
newdata$remarry_right <- as.factor(newdata$remarry_right)
newdata$judgment_divorce <- as.factor(newdata$judgment_divorce)
```


# split the data
```{r}
newdata_exCY<- newdata[,-c(1,2)]
train_sample <-createDataPartition(newdata_exCY$Marriage_rate,p = 0.8, list = F)
train_data <- newdata_exCY[train_sample,]
test_data <- newdata_exCY[-train_sample,]
```

# Model without country and year
```{r}
newfit1 <- lm(Marriage_rate~., data = train_data)
summary(newfit1)
```

# Agian, remove some insignificant variables
```{r}
newfit2 <- lm(Marriage_rate~Male_Life_Expectancy
              +female_Life_Expectancy + GDP+Births_outside_marriage 
              + Divorce_rate+births_per_woman+Population_est + judgment_divorce, data = train_data)
summary(newfit2)
```

# VIF
```{r}
VIF_art3 <- data.frame(car::vif(newfit2))
VIF_art3 %>% kbl() %>% kable_styling(bootstrap_options = "striped", 
                                          full_width = F, position = "center")
```


# So again, remove male life expectancy
```{r}
newfit3 <- lm(Marriage_rate~female_Life_Expectancy + GDP+Births_outside_marriage 
              + Divorce_rate+births_per_woman+Population_est + judgment_divorce, data = train_data)
summary(newfit3)

```


# Interactive term
```{r}
newfit4 <- lm(Marriage_rate~(female_Life_Expectancy + GDP+Births_outside_marriage 
              + Divorce_rate+births_per_woman+Population_est + judgment_divorce)^2, data = train_data)
summary(newfit4)

```



# Check the model
```{r}
pre1 <- newfit1 %>% predict(test_data)
p1 = data.frame(RMSE = RMSE(pre1, test_data$Marriage_rate),R2 = R2(pre1,test_data$Marriage_rate))

pre2 <- newfit2 %>% predict(test_data)
p2 = data.frame(RMSE = RMSE(pre2, test_data$Marriage_rate),R2 = R2(pre2,test_data$Marriage_rate))

pre3 <- newfit3 %>% predict(test_data)
p3 = data.frame(RMSE = RMSE(pre3, test_data$Marriage_rate),R2 = R2(pre3,test_data$Marriage_rate))

pre4 <- newfit4 %>% predict(test_data)
p4 = data.frame(RMSE = RMSE(pre4, test_data$Marriage_rate),R2 = R2(pre4,test_data$Marriage_rate))
```


```{r}
all2 = rbind(p1,p2,p3,p4)
# add F-statistic
all2 = cbind(all2, c(summary(newfit1)$fstatistic[1],summary(newfit2)$fstatistic[1],summary(newfit3)$fstatistic[1],summary(newfit4)$fstatistic[1]))
# add adj r squared
all2 = cbind(all2, c(summary(newfit1)$adj.r.squared,summary(newfit2)$adj.r.squared,summary(newfit3)$adj.r.squared,summary(newfit4)$adj.r.squared))
#add RSE
all2 = cbind(all2, c(summary(newfit1)$sigma,summary(newfit2)$sigma,summary(newfit3)$sigma,summary(newfit4)$sigma))

all2 = cbind(c('fit1','fit2','fit3','fit4'),all2)
colnames(all2)[c(1,4,5,6)] <- c('models','F stat', 'adj.r2','RSE')

all2
```


# Best subset????

```{r}
bestfit <- regsubsets(Marriage_rate~.,train_data)
bestfit_summary <- summary(bestfit)

bestfit_summary

```


```{r}
data.frame(Adj.R2 = which.max(bestfit_summary$adjr2),
           CP = which.min(bestfit_summary$cp),
           BIC = which.min(bestfit_summary$bic))
```


# So final model would be newfit3 model, use stargazer
```{r}
stargazer::stargazer(newfit3,type = "html", summary = TRUE, report = "vc*stp", ci = TRUE)
```


```{r}
sjPlot::tab_model(newfit3)
```




